biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-10-11 paper/PaperTRA/PaperTRA.Rmd
Add minor tweak

Our findings suggest that a bicycle and PT combination could viably replace 20% of current LMA trips, with an additional 12% of PT journeys prone to further substitution. 
<!-- repeated? not correct -->

>>>>

Our findings suggest that cycling and PT *in combination* could viably replace 20% of current LMA trips, with an additional 12% of PT journeys prone to further substitution. 
<!-- repeated? not correct -->
